Weather Data Integration and Assimilation System\\

### 2020-02-11 method/sec_3-microservice.tex
Reviewed again after PGS reject

The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often an HTTP resource API. These services are built around business capabilities and independently deployable by fully automated deployment machinery. There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies \cite{LewisMicroservices}.

Among the characteristics of \acrfull{microservice}, few characteristics heavily affect while moving from \acrshort{soa} to \acrshort{microservice}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Smart Endpoints And Dumb Pipes}
\label{subse:dumb_pipes}
When building communication endpoints, many architecture approach with putting significant smart into the communication mechanism. One good example is \acrshort{esb} what we discussed in section \ref{se:architectural_decisions}. But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built from microservices aim to be as decoupled and as cohesive as possible. They own their own domain logic and act more as filters in the classical Unix sense. After receiving a request, applying logic as appropriate and producing a response. And it uses simple RESTish protocols rather than complex protocols.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pattern: Database per Service}
\label{subse:database_per_service}
- Pattern: Database per service

@@

Keep each microservice’s persistent data private to that service and accessible only via its API. 
There are a few different ways to keep a service’s persistent data private. You do not need to provision a database server for each service. For example, if you are using a relational database then the options are \cite{RichardsonMicroservicesService}:
\begin{itemize}
    \item \emph{Private-tables-per-service} – each service owns a set of tables that must only be accessed by that service
    \item \emph{Schema-per-service} – each service has a database schema that’s private to that service
    \item \emph{Database-server-per-service} – each service has its own database server.
\end{itemize}
Private-tables-per-service and schema-per-service have the lowest overhead. Using a schema per service is appealing since it makes ownership clearer. Some high throughput services might need their own database server.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pattern: Sagas}
\label{subse:sagas}
In order to ensure loose coupling, each service has its own database. Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications. An application must instead use the Saga pattern. A service publishes an event when its data changes. Other services consume that event and update their data \cite{RichardsonMicroservicesSagas}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Scale Cube}
\label{subse:scale_cube}
The scalability of a system can explain via a concept called \emph{Scale Cube} which talk about the scalability of the application throw X, Y and Z axis.

\subsubsection{X-axis Saling}
X-axis scaling consists of running multiple copies of an application behind a load balancer. If there are N copies then each copy handles 1/N of the load. This is a simple, commonly used approach of scaling an application TODO.

\subsubsection{Y-axis Scaling}
Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
\begin{itemize}
    \item verb-based decomposition ex: checkout.
    \item decompose the application by noun ex: customer management. 
    \item An application might use a combination of verb-based and noun-based decomposition.
\end{itemize}

@@

\subsubsection{Z-axis Scaling}
When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Brief introduction to the \acrfull{k8s}}
\label{sebse:k8s_intro}

\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
Components of \acrshort{k8s},
\begin{itemize}
    \item Pods – Cluster of containers that can group other container images in a single unit.
    \item Nodes - the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
    \item kubelet - An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy - A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master - Responsible for maintaining the desired state for your cluster.
    \item etcd - Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}
Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
In the figures of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represent a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture for server requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}
In left side of the figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side show the export modules. As it explained section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database in order to fast access as mentioned in section \ref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handle request asynchronously}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.

As shown in the figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. But as shown in figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not. Here is uses the microservice pattern of \ref{subse:sagas} while processing the Grid data. First it store the data and respond back to the user. Then publish an event, and another service listen to those events and process the data and update the system status.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation \acrshort{wdias} microservices}
    \label{fi:wdias_micro_separation}
\end{figure}
The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}. As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
Apart from that, as we further discuss in section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} API Convention}
\label{sebse:wdias_api}
One of the main design consideration in \acrshort{wdias} is the convention of defining the APIs. It follows the simple RESTful API, and allow users to interact with HTTP methods.

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \emph{GET /parameter} - Get parameters
        \item \emph{POST /parameter} - Create parameter
        \item \emph{PUT /parameter/id} - Update parameter
        \item \emph{DELETE /parameter/id} - Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \emph{GET timestep} - Get TimeSteps
        \item \emph{POST timestep} - Create TimeStep
        \item \emph{PUT timestep/id} - Update TimeStep
        \item \emph{DELETE timestep/id} - Delete TimeStep
    \end{itemize}
    \item location
    \begin{itemize}
        \item \emph{GET /location} - Get location points
        \item \emph{POST /location} - Create location point
        \item \emph{PUT /location/id} - Update location point
        \item \emph{DELETE /location/id} - Delete location point
        \item \emph{GET /location/regular-grid} - Get regular grids
        \item \emph{POST /location/regular-grid} - Create regular grid
        \item \emph{PUT /location/regular-grid/id} - Update regular grid
        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \emph{GET /timeseries} - Get timeseries
        \item \emph{POST /timeseries} - Create timeseries
        \item \emph{PUT /timeseries/id} - Update timeseries
        \item \emph{DELETE /timeseries/id} - Delete timeseries
    \end{itemize}
\end{itemize}

@@

The API convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE}  allows users to integrate new import or export modules into the system as well as add new data types.

>>>>

The microservice architectural style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often \hl{an HTTP resource API}. These services are built around business capabilities and independently deployable by fully automated deployment machinery. \hl{There is a bare minimum of centralized management of these services, which may be written in different programming languages and use different data storage technologies} \cite{LewisMicroservices}.

\hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
\dbc{M in Microservice should be capitalized only on begining of a sentence.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Smart Endpoints and Dumb Pipes}
\label{subse:dumb_pipes}
\dbc{At the end of previous para tell what will be discussed in the next set of sub-section. A single sentence like "Next, we will discusss ...." is enough}

When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in section \ref{se:architectural_decisions}. But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built from microservices aim to be as decoupled and as cohesive as possible. They own their own domain logic and act more as filters in the classical Unix sense. After receiving a request, applying logic as appropriate and producing a response. And it uses simple RESTish protocols rather than complex protocols.
\dbc{RESTish or RESTful?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Pattern: Database per Service}}
\label{subse:database_per_service}
\hl{- Pattern: Database per service}

@@

Keep each microservice’s persistent data private to that service and accessible only via its API. 
There are a few different ways to keep a service’s persistent data private. You do not need to provision a database server for each service. For example, if you are using a relational database then the options are \cite{RichardsonMicroservicesService}:
\begin{itemize}
    \item \emph{Private-tables-per-service} –- each service owns a set of tables that must only be accessed by that service
    \item \emph{Schema-per-service} –- each service has a database schema that’s private to that service
    \item \emph{Database-server-per-service} -– each service has its own database server.
\end{itemize}
Private-tables-per-service and schema-per-service have the lowest overhead. Using a schema per service is appealing since it makes ownership clearer. Some high throughput services might need their own database server.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Pattern: Sagas}}
\label{subse:sagas}
In order to ensure loose coupling, each service has its own database. Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications. An application must instead use the Saga pattern. A service publishes an event when its data changes. Other services consume that event and update their data \cite{RichardsonMicroservicesSagas}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{The Scale Cube}}
\label{subse:scale_cube}
The scalability of a system can explain via a concept called \emph{Scale Cube} which talk about the scalability of the application throw X, Y and Z axis.

\paragraph{x-axis Saling}-- x-axis scaling consists of running multiple copies of an application behind a load balancer. If there are \textit{n} copies then each copy handles 1/\textit{n} of the load. This is a simple, commonly used approach of scaling an application \hl{TODO}.

\paragraph{y-axis Scaling}-- Unlike x-axis and x-axis, which consist of running multiple, identical copies of the application, y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
\begin{itemize}
    \item verb-based decomposition ex: checkout.
    \item decompose the application by noun, for e.g., customer management. 
    \item An application might use a combination of verb-based and noun-based decomposition.
\end{itemize}

@@

\\paragraph{Z-axis Scaling}-- When using x-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Brief introduction to the \acrfull{k8s}}
\label{sebse:k8s_intro}
\dbc{Don't present this as a separate section. Either this need to be in the literature survey, or integrate key ideas into another section as a paragraph.}

\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
Components of \acrshort{k8s},
\begin{itemize}
    \item Pods -- Cluster of containers that can group other container images in a single unit.
    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}
Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of Figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in section \ref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.

As shown in Figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. However, as shown in Figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not. Here is uses the microservice pattern of \ref{subse:sagas} while processing the Grid data. First it store the data and respond back to the user. Then publish an event, and another service listen to those events and process the data and update the system status.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation of \acrshort{wdias} microservices.}
    \label{fi:wdias_micro_separation}
\end{figure}
The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}. As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
Apart from that, as we further discuss in section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} API}
\label{sebse:wdias_api}
One of the main design consideration in \acrshort{wdias} is the convention of defining the APIs. It follows the simple RESTful API, and allow users to interact with HTTP methods.

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \texttt{GET /parameter} -- Get parameters
        \item \texttt{POST /parameter} -- Create parameter
        \item \texttt{PUT /parameter/id} -- Update parameter
        \item \texttt{DELETE /parameter/id} -- Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \texttt{GET timestep} -- Get TimeSteps
        \item \texttt{POST timestep} -- Create TimeStep
        \item \texttt{PUT timestep/id} -- Update TimeStep
        \item \texttt{DELETE timestep/id} -- Delete TimeStep
    \end{itemize}
\dbc{Format others as above}
    \item location
    \begin{itemize}
        \item \emph{GET /location} - Get location points
        \item \emph{POST /location} - Create location point
        \item \emph{PUT /location/id} - Update location point
        \item \emph{DELETE /location/id} - Delete location point
        \item \emph{GET /location/regular-grid} - Get regular grids
        \item \emph{POST /location/regular-grid} - Create regular grid
        \item \emph{PUT /location/regular-grid/id} - Update regular grid
        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \emph{GET /timeseries} - Get timeseries
        \item \emph{POST /timeseries} - Create timeseries
        \item \emph{PUT /timeseries/id} - Update timeseries
        \item \emph{DELETE /timeseries/id} - Delete timeseries
    \end{itemize}
\end{itemize}

@@

The API convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE}}  allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-11 method/sec_5-data_preprocess.tex
Change to fi: label
Removed commercial database names
Reviewed again after PGS reject

\section{Extensions (Weather Data Prepossessing)}
\dbc{Section title?}

The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{Weather Data Preprocessing}
    \label{fig:weather_data_preprocessing}
\end{figure}
The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
constant at the time of creating new triggers for an extension.

@@

\subsubsection{Serial Interpolation}
In serial interpolation mode, interpolation is done to fill any gaps in a time series. The interpolation module will only consider the time series itself in filling these gaps.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/serial_interpolation.jpg}
    \caption{Serial Interpolation}
    \label{fig:serial_interpolation}
\end{figure}

\subsubsection{Spatial Interpolation}
In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from time series data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
    \caption{Spatial Interpolation}
    \label{fig:spatial_interpolation}
\end{figure}

\subsection{Transformation}
Simple arithmetic manipulation, Time interval transformation and Shifting the series in time
Specific hydro-meteorological transformation such as stage discharge relationships
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
    \caption{Transformation}
    \label{fig:transformation}
\end{figure}

\subsection{Validation}
Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Validation}
    \label{fig:validation}
\end{figure}

\subsection{Extension API}
In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
\begin{lstlisting}[language=Python]
{
    "extensionId": "",
    "extension": "Interpolation/Transformation/Validation",
    "function": "",
    "variables": [
        {
            "variableId": "",
            "metadata/metadtaIds": {
            }
        }
    ],
    "inputVariables": [],
    "outputVariables": [],
    "trigger": [
        {
            "trigger_type": "OnChange/OnTime",
            "trigger_on": []
        }
    ],
    "options": {
    }
}
\end{lstlisting}
\begin{itemize}
    \item extensionId - An unique identifier for new extension trigger. Should be unique among all extensions.
    \item extension - The main extension category which is responsible for handling the extension with extracting data required and storing the output. Interpolation/Transformation/Validation support for the moment.
    \item function - Name of the microservice which is handling the input to output mapping. Fn() function in the \ref{fig:weather_data_preprocessing}.
    \item variables - Array timeseries mapping to variables. Multiple variables can be define with metadata or metadataIds of timeseries. Can be use same variable on inputVariables and outputVariables below.
    \item inputVariables - Timeseries that need to be provide into the function
    \item outputVariables - Timeseries that output from the function
    \item trigger - Type of trigger for the extension. Should be one of OnTime or OnChange.
    \begin{itemize}
        \item trigger - OnChange
        \item trigger\_on - List of timeseries to listen on change and trigger the extension
    \end{itemize}
    \begin{itemize}
        \item trigger - OnTime
        \item trigger\_on - List of schedules that need to be trigger the extension in cronjob string format
    \end{itemize}
    \item options - Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
\end{itemize}

\subsubsection{Extension Handler}
Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's OnChange timeseries.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Extension Handler}
    \label{fig:extension_handler}
\end{figure}

In further elaboration, when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler. Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.

In order to improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms. For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint.
First, other than storing extension metadata in MySQL instance of adapter-extension, it also store the data in reverse lookup table called triggers. Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries. Thus the response which is received by the 
extension-handler only contains the extensions to be triggered. No additional filtering need to be done at the extension-handler service.
Second, cache the resulting trigger\_type and timeseries data in \acrshort{redis} database for fast access and avoid too much queries on \acrshort{mysql} database.

\subsubsection{Extension Scheduler}
Extension Handler is responsible for triggering the correct Extension with metadata at given time which is provided at the creation on extension trigger's with the value of OnTime cronjob string value.

In order to improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
Same as for extension-handler, the adapter-extension expose an endpoint to retrieve extension metadata grouped by cronjob time. Then use \acrshort{go} to implement the extension-handler to fast processing the extensions. After retrieve extension which are grouped by cronjob time; within the extension-handler, it schedules programatic cronjobs to trigger at given times. When each cronjob triggers at given time, it also contains the extensions to be triggered. Fetching extension data and creating cronjobs occur with long period of time in order to avoid heavy overhead.
When a new extension trigger created, those data push into a \acrshort{redis} List. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
As mentioned above, in order to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in long period of time and flush the previously scheduled cronjobs.
The extension-handler should be run as a single entity for the atrocity, in order to avoid triggering same extension twice.

>>>>

\section{Data Prepossessing}

The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Weather data preprocessing}}
    \label{fi:weather_data_preprocessing}
\end{figure}

The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
constant at the time of creating new triggers for an extension.

@@

\paragraphSerial Interpolation}-- In serial interpolation mode, interpolation is done to fill any gaps in a time series. The interpolation module will only consider the time series itself in filling these gaps.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/serial_interpolation.jpg}
    \caption{Serial interpolation.}
    \label{fi:serial_interpolation}
\end{figure}

\paragraph{Spatial Interpolation}-- In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from time series data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

\subsection{Transformation}-- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
    \caption{\hl{Transformation}}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}-- Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{\hl{Validation}}
    \label{fi:validation}
\end{figure}

\subsection{\hl{Extension API}}
In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
\begin{lstlisting}[language=Python]
{
    "extensionId": "",
    "extension": "Interpolation/Transformation/Validation",
    "function": "",
    "variables": [
        {
            "variableId": "",
            "metadata/metadtaIds": {
            }
        }
    ],
    "inputVariables": [],
    "outputVariables": [],
    "trigger": [
        {
            "trigger_type": "OnChange/OnTime",
            "trigger_on": []
        }
    ],
    "options": {
    }
}
\end{lstlisting}
\begin{itemize}
    \item extensionId -- An unique identifier for new extension trigger. Should be unique among all extensions.
    \item extension -- The main extension category which is responsible for handling the extension with extracting data required and storing the output. Interpolation/Transformation/Validation support for the moment.
    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the \ref{fi:weather_data_preprocessing}.
    \item variables -- Array timeseries mapping to variables. Multiple variables can be define with metadata or metadataIds of timeseries. Can be use same variable on inputVariables and outputVariables below.
    \item inputVariables -- Timeseries that need to be provide into the function
    \item outputVariables -- Timeseries that output from the function
    \item trigger -- Type of trigger for the extension. Should be one of OnTime or OnChange.
    \begin{itemize}
        \item trigger -- OnChange
        \item trigger\_on -- List of timeseries to listen on change and trigger the extension
    \end{itemize}
    \begin{itemize}
        \item trigger -- OnTime
        \item trigger\_on -- List of schedules that need to be trigger the extension in cronjob string format
    \end{itemize}
    \item options -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
\end{itemize}

\subsubsection{Extension Handler}
Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's OnChange timeseries.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Extension handler.}
    \label{fi:extension_handler}
\end{figure}

\hl{In further elaboration,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler. Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.

To improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms. For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint. First, other than storing extension metadata in MySQL instance of adapter-extension, it also store the data in reverse lookup table called triggers. Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries. Thus, the response which is received by the 
extension-handler only contains the extensions to be triggered. No additional filtering need to be done at the extension-handler service.
Second, cache the resulting trigger\_type and timeseries data in \acrshort{redis} database for fast access and avoid too much queries on \acrshort{mysql} database.

\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at given time which is provided at the creation on extension trigger's with the value of OnTime cronjob string value. To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
Same as for extension-handler, the adapter-extension expose an endpoint to retrieve extension metadata grouped by cronjob time. Then use \acrshort{go} to implement the extension-handler to fast processing the extensions. After retrieve extension which are grouped by cronjob time; within the extension-handler, it schedules programatic cronjobs to trigger at given times. When each cronjob triggers at given time, it also contains the extensions to be triggered. Fetching extension data and creating cronjobs occur with long period of time in order to avoid heavy overhead.
When a new extension trigger created, those data push into a \acrshort{redis} List. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
As mentioned above, in order to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in long period of time and flush the previously scheduled cronjobs.
The extension-handler should be run as a single entity for the atrocity, in order to avoid triggering same extension twice.
